\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsthm}
\usepackage{enumitem} 
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\author{Ding Yaoyao}
\title{Mathematical Logic Homework 8}

\newenvironment{sol}[1]
{\par\vspace{3mm}\noindent{\it Solution #1}.}
{\qed}

\newenvironment{thm}[1]
{\par\vspace{3mm}\noindent{\textbf{#1}}.\quad}{\\\\}

\newcommand{\abs}[1]{\lvert#1\rvert}
\newcommand{\fA}{\mathfrak{A}}
\newcommand{\fB}{\mathfrak{B}}
\newcommand{\fC}{\mathfrak{C}}
\newcommand{\fI}{\mathfrak{I}}
\newcommand{\fJ}{\mathfrak{J}}
\newcommand{\fT}{\mathfrak{T}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\begin{document}
	\maketitle
	
	\begin{sol}{8.1}
		(1) Wrong
			
			If it's correct, by (2), we can get the equivalence of decidability and enumerability. But it's wrong as discussed in class.
			
		(2) Correct
		
			$\Rightarrow$: We can enumerate all the elements of $A^*$ by increasing order of length, and decide whether the element belongs to $W$. If it belongs to $W$, we print it, otherwise not. 
			
			$\Leftarrow$: We can strictly enumerate the elements in $W$ and when the element we want to decide occurs, halts and when the length exceeds the length of element we want to decide, prints anything and halts.
	\end{sol}

	\begin{sol}{8.2}
		Prove by contradiction.
		
		Assume it's R-decidable and the program $\mathcal{P}_0$ can decide the set.
	
		For all program $\mathcal{P}$, construct a mapping:$\mathcal{P}\rightarrow\mathcal{P^+}$ such as
		\begin{verbatim}
		if r0 not empty then
		    loop forever
		else
		    call P
		fi
		\end{verbatim}
		(I write the program in pseudo code and the same program of register machine version must exist)
		
		Then we can construct a program $\mathcal{P}_1$ that can decide $\Pi_{halt}$ such as
		\begin{verbatim}
		get w_P+ from w_P and store it to r0
		call P0
		\end{verbatim}
		Then the above program $\mathcal{P}_1$ can decide $\Pi_{halt}$, which is a contradiction.
		
		In conclusion, the set in the problem statement is not decidable.
	\end{sol}

\end{document}